Stylistic Context Clustering for Token-Level Author Diarization

### 2018-01-06 paper/paper.tex
Fixed an error

\name{Ivan Grubišić, Milan Pavlović, Mate Šimović}

\address{
University of Zagreb, Faculty of Electrical Engineering and Computing\\
Unska 3, 10000 Zagreb, Croatia\\ 
\texttt{\{ivan.grubisic, milan.pavlovic, mate.simovic\}@fer.hr}\\
}

\abstract{ 
In this paper we present an approach to tackle the PAN 2016 author diarization and intrinsic plagiarism detection problem. We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window. There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt it for clustering with a trainable feature transformation. We have evaluated our approach on the available datasets from PAN 2016.
}

>>>>

\name{Ivan Grubišić, Milan Pavlović}

\address{
University of Zagreb, Faculty of Electrical Engineering and Computing\\
Unska 3, 10000 Zagreb, Croatia\\ 
\texttt{\{ivan.grubisic, milan.pavlovic\}@fer.hr}\\
}

\abstract{ 
In this paper we present an approach to tackle the PAN 2016 author diarization and intrinsic plagiarism detection problem. We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window. There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adapt it for clustering with a trainable feature transformation. We have evaluated our approach on the available datasets from PAN 2016.
}
